Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-30 dit-paper_ieee.tex

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3, 4 and 5.
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}

>>>>

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3, 4 and 5.
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}
